---
title: "Kresge Final"
output: word_document
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
sys.source("Non_writing_functions.R", envir = knitr::knit_global())
```

**Steps for the Analysis:**

1.  Pull Full Datasets from Attune
    -   Pre and Post are saved in different folders
2.  Run Folder("Full Data") through Kresge_auto_agg_to_excel.R
    -   Argument can be changed at "summary_data \<- XXX"
    -   sum_up gives the 5numsum of all files
    -   do_both(combine_variables(data)) does and hour average for all
        files
    -   Update input folder name and output folder name as needed
3.  Do_Both creates a .xlsx file where each location gets its own sheet
    1.  sum_up does this as well
4.  For use, run the do_both file through the mulitplesheets() function
    1.  This will load the individual sheets to R

```{r load_in, echo=FALSE, include=FALSE}

path_post <- "~/Kresge/Data/PostReno/Post_do_both_5_31.xlsx"
my_sheets = multiplesheets(path_post)
similar_columns_post <- c("Temp", "Hum", "Dioxide", "Organic", "PM2.5", "PM10", "HCHO", "Monoxide")
post_reno <- combine_similar_columns(my_sheets, similar_columns_post)


path_pre <- "~/Kresge/Data/PreReno/Prer_do_both_5_31.xlsx"
my_sheets = multiplesheets(path_pre)
similar_columns_pre <- c("Temp", "Hum", "CO2", "PM2.5", "PM10")
pre_reno <- combine_similar_columns(my_sheets, similar_columns_pre)


merged_df <- merge(post_reno, pre_reno, by = "ID")

```

```{r subsetting, echo=FALSE, include=FALSE}
library(tidyr)
long_subset_maker <- function(test_var,df){

  test_subset <- subset(merged_df, select = c("ID", grep(test_var, names(df), value = TRUE)))

  test_subset <- colClean(test_subset)

  test_names <- names(test_subset[-1])

  test_subset_long <- pivot_longer(test_subset, 
                                 cols = all_of(test_names), 
                                 names_to = "variable", 
                                 values_to = "Test_var")

  # Create a new column indicating whether it's Pre or Post
  test_subset_long$Type <- ifelse(grepl("Prer", test_subset_long$variable), "Pre", "Post")
  test_subset_long$Location <- ifelse(grepl("Albany", test_subset_long$variable),"Albany",
                                    ifelse(grepl("Conyers", test_subset_long$variable), "Conyers",
                                           ifelse(grepl("Peachtree_Tower", test_subset_long$variable), "Peachtee_Tower",
                                                  ifelse(grepl("Milledgeville", test_subset_long$variable), "Milledgeville",
                                                         ifelse(grepl("East_Lake", test_subset_long$variable), "East_Lake",
                                                                ifelse(grepl("Lucy_Morgan",
                                                                             test_subset_long$variable),"Lucy_Morgan","Griffin"))))))
  return(test_subset_long)
}
```

```{r comparison_subsets, echo = FALSE, include=FALSE}
temp_long_subset <- long_subset_maker("Temp",merged_df)
hum_long_subset <- long_subset_maker("Hum", merged_df)
co2_long_subset <- long_subset_maker("CO2|Dioxide", merged_df)
pm2.5_long_subset <- long_subset_maker("PM2.5", merged_df)
pm10_long_subset <- long_subset_maker("PM10", merged_df)

```

```{r plot_functions, echo= FALSE, include=FALSE}
library(ggplot2)
my_colors <- c("red", "blue", "green", "#FF7F00", "purple", "yellow","#F781BF")

# Set linetype based on the Type column
comp_plot <- function(long_ss, threshold, title){
  ggplot(long_ss, aes(x = ID, y = Test_var, color = Location, linetype = Type)) +
  geom_line(size = 1) +
  ggtitle(title)+
  geom_hline(yintercept = threshold, linetype = "dashed", color = "red") +
  labs(color = "Location") +
  scale_color_manual(values = my_colors) +
  scale_linetype_manual(values = c("dashed", "solid"))
  }
```

```{r comparison_plots, fig.align='center', warning=FALSE}
comp_plot(temp_long_subset, 74, "Temperture Comparison")
comp_plot(hum_long_subset, 70, "Humidity Comparison")
comp_plot(co2_long_subset, 2001, "Co2 Comparison")
comp_plot(pm2.5_long_subset, 55.5, "Pm2.5 Comparison")
comp_plot(pm10_long_subset, 255, "Pm10 Comparison")
comp_plot(pm10_long_subset, 255, "Pm10 Comparison")
```

